---
title: "inital work"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
```

Loading data and doing some preliminary exploration.

I think one part of this would be some factor engineering to create something that could take into account the weather data. 


Reading the data:

```{r}
weather_train <- read_csv("data/weather_test.csv")
```


## EDA

Getting some summaries of the data 

I want a plot of an the average temperature, let's pick July, average temperature for each hour for the entire month

```{r}
wthr <- weather_train %>% filter(month(timestamp) == 7) %>% 
  mutate(day. = day(timestamp), hr = hour(timestamp)) %>% 
  group_by(site_id, day., hr) %>% 
  summarize(avg_hr_temp = mean(air_temperature))
```


### what about the distribution of sites and buildings? 

```{r}
metabldg <- read_csv("data/building_metadata.csv") 
```

so how do sites and buildings break down?

```{r}
metabldg %>% group_by(site_id) %>% 
  summarize(counts = n())
```
  

Site representation

```{r}
metabldg %>% group_by(site_id) %>% 
  summarize(counts = n()) %>% 
  ggplot(aes(x = site_id, y = counts)) + 
  geom_bar(stat = "identity")
```



